% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{comment}

% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Shinpei Kato}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  Dept. of Information Engineering\\
  Nagoya University\\
  Furo-cho, Chikusa-ku, Nagoya 464-8603, JAPAN\\
\end{minipage}
\hspace{1em}
\begin{minipage}[t]{0.5\textwidth}
  Email: \href{mailto:shinpei@is.nagoya-u.ac.jp}{\tt
 shinpei@is.nagoya-u.ac.jp} \\
  Web: \href{http://www.ertl.jp/~shinpei/}{\tt
 http://www.ertl.jp/\~{}shinpei/} \\
  Phone: +81-52-789-4597 \\
\end{minipage}

\section*{RESEARCH INTERESTS}

\begin{itemize}

 \item My research interests include cyber-physical systems and parallel
       and distributed systems with a particular emphasis on operating
       systems and system software.
\end{itemize}

\section*{EDUCATION}

\begin{itemize}

  \item B.S. Dept. of Information and Computer Science, Keio
	University, 2004.

  \item M.S. Graduate School of Science and Technology, Keio
	University, 2006.

  \item Ph.D. Graduate School of Science and Technology, Keio
	University, 2008.\\
\end{itemize}

\section*{PROFESSIONAL EXPERIENCE}

\begin{itemize}

\item \textbf{Associate Professor}, Dept. of Information
      Engineering, Nagoya University. Apr 2012 - Present.

\item \textbf{Research Scientist}, Dept. of Computer Science,
      University of California, Santa Cruz. Jul 2011 - Mar 2012.

\item \textbf{Visiting Scientist}, Dept. of Electrical and
      Computer Engineering, Carnegie Mellon University, Sep 2009 - Jun
      2011.

\item \textbf{Research Scientist}, Dept. of Computer Science, The
      University of Tokyo. Apr 2009 - Jun 2011.

\item \textbf{Research Scientist}, Dept. of Information and
      Computer Science, Keio University. Apr 2008 - Mar 2009.

\end{itemize}

\section*{SELECTED PUBLICATIONS}

\begin{enumerate}
 \item Y. Abe, H. Sasaki, S. Kato, K. Inoue, M. Edahiro,
       M. Peres. "Power and Performance Characterization and Modeling of
       GPU-accelerated Systems", In Proceedings of the 28th IEEE
       International Parallel and Distributed Processing Symposium
       (IPDPS'14), 2014.

 \item  J. Augusto, G. Lima, K. Bletsas, and S. Kato. "Multiprocessor
	Real-Time Scheduling with a Few Migrating Tasks", In Proceedings
	of the 34th IEEE Real-Time Systems Symposium (RTSS'13), pp. 170
	- 181, 2013.

 \item M. Hirabayashi, S. Kato, M. Edahiro, K. Takeda, T. Kawano, and
       S. Mita. "GPU Implementations of Object Detection using HOG
       Features and Deformable Models", In Proceedings of the 1st IEEE
       International Conference on Cyber-Physical Systems, Networks, and
       Applications (CPSNA'13), 2013.

 \item S. Kato, J. Aumiller, and S. Brandt. "Zero-Copy I/O Processing
       for Low-Latency GPU Computing", In Proc. of the 4th ACM/IEEE
       International Conference on Cyber-Physical Systems 
       (ICCPS'13), pp. 170-178, 2013.

 \item R. Davis and S. Kato. "FPSL, FPCL and FPZL Schedulability
       Analysis", Real-Time Systems, Vol. 48, No. 6, pp. 750-788, 2012.

 \item S. Kato, M. McThrow, C. Maltzahn, and S. Brandt. "Gdev:
       First-Class GPU Resource Management in the Operating System", In
       Proc. of the 2012 USENIX Annual Technical Conference
       (USENIX ATC'12), 2012.

 \item D. Skourtis, S. Kato, and S. Brandt. "QBox: Guaranteeing I/O
       Performance on Black Box Storage Systems", In Proceedings of the
       21st ACM Symposium on High-Performance Parallel and Distributed
       Computing (HPDC'12), pp. 73-84, 2012.

 \item S. Kato, K. Lakshmanan, A. Kumar, M. Kelkar, Y. Ishikawa, and
       R. Rajkumar. "RGEM: A Responsive GPGPU Execution Model for
       Runtime Engines", In Proceedings of the 32nd IEEE Real-Time
       Systems Symposium (RTSS'11), pp. 57-66, 2011.

 \item S. Kato, K. Lakshmanan, R. Rajkumar, and Y. Ishikawa. "TimeGraph:
       GPU Scheduling for Real-Time Multi-Tasking Environments", In
       Proceedings of the 2011 USENIX Annual Technical Conference
       (USENIX ATC'11), 2011.

 \item S. Kato, Y. Ishikawa, and R. Rajkumar. "CPU Scheduling and Memory
       Management for Interactive Real-Time Applications", Real-Time
       Systems, Vol. 47, No. 5, pp. 454 - 488, 2011.
\end{enumerate}


% Footer
%\begin{center}
%  \begin{small}
%   %Last updated: \today
%  \end{small}
%\end{center}

\end{document}
